Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-26 paper/ijcai/paper.tex
comments
pass on threats to validity

@@

\Mar{-------------------------- estou aqui}

@@

\subsection{Threats to validity}
%
A potential threat to \textit{external validity} related to the set of programs used in
our study. When choosing the projects for our study, our aim was to opt for
projects that resemble a general and large-sized application. To reduce
selection bias and facilitate the comparison of our results, we decided to
choose a benchmark that is popular in the community~\cite{just-defects4j-issta2014}.
It is importance to notice that our study does not evaluate the fault of the \closure{}
project since it requires high CPU to perform the \combpar{k} evaluation. A potential
threat to \textit{construct validity} relates to the choice of oracle generation
for the Lithium toolset. However, we argue that our choice is able to capture whether
a program is failing because of the same reason.
The main threat to \textit{internal validity} lies in the complexity of several of the tools
used in our experiments, most notably the Lithium toolset, the SFL diagnosis tool,
and the implementation of \comb{}.
%
\section{Related Work}

>>>>

\Mar{Sofia, vc. precisa revisar com mais cuidado os dois proximos paragrafos...}

@@

@@

\subsection{Threats to validity}
%
A potential threat to \textit{external validity} relates to the set of programs used in
our study. When choosing the projects for our study, our aim was to opt for
projects that resemble a general and large-sized application. To reduce
selection bias and facilitate the comparison of our results, we decided to
choose a benchmark that is popular in the community~\cite{just-defects4j-issta2014}.
Our study did not evaluate the faults from the \closure{}
project because of the high CPU cost of running \combpar{k} on it. A potential
threat to \textit{construct validity} relates to the choice of oracle
we used for the Lithium slicer. We found empirically that our choice was able to capture 
the faults for the cases we analyzed.
The main threat to \textit{internal validity} lies in the complexity of several of the tools
used in our experiments, most notably the Lithium toolset, the SFL diagnosis tool,
and the implementation of \comb{}. To mitigate this threat, we
carefully inspected our code and looked for discrepancies and
incoherences in our results.

%
\section{Related Work}
